---
title: "Developing Data Products Course Project"
author: "Panagiotis Pramangioulis"
date: "May 30, 2018"
output:
  slidy_presentation:
    self_contained: no
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This presentation is part of the Developing Data Products Coursera.org course project submission.

It is an R Presentation generated with RStudio.

The Shiny application pitched by this presentation is at https://ppramang.shinyapps.io/myapp/.

The Shiny app source code is available at https://github.com/ppramang/developing_data_products_course_project.


## What is the purpose of the developed Shiny app?

The *Iris Quick Exploratory Analysis Shiny app* develops a generic exploratory analysis of an iris flower both a individual flower and species level. Below you can have a look of what the iris dataset contains:

```{r, echo=TRUE}
head(iris)
```


## What is the Content of the *Iris Quick Exploratory Analysis Shiny app*

- This App has 2 sections, a sidebar which is on the left of the App and on the right is main screen that contains   the tabs.  
- The sidebar panel have four(4) control items.  
- Title textbox allow user to customize the main page title description.  
- The second control item allows the user to select the continuous variable, that he wants to be displayed and     
  analysed
- The third item is to control how many observatrions will be showed under the Table tab.  
- The forth item allows the user to select the displayed color of the histogram.  
- On the Main Page, there are 5 tabs:  
      1. The first tab displays the histogram of the dataset selected.  
      2. The second tab show the summary  
      3. The third tab shows the observations. The no of observations displayed is based on the number selected by user     in the slidebar.
      4. The forth tab displays the dataset structure.
      5. The fifth tab constitutes the Documentation of the developed data product"


##Ready to give it a try?

Use the Shiny app at https://ppramang.shinyapps.io/myapp/

Get the app source code at https://github.com/ppramang/developing_data_products_course_project.

